Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-03-21 doc/tfp-2011/main.tex
conclusions updated [KK]

We presented a distributed programming environment for functional
programming. The main features are the genericity of the interface,
which makes use of polymorphic higher-order functions, and the ability
to easily switch between sequential, multi-core, and network
implementations. In particular, \functory\ allows to use the same
executable for master and workers, which makes the deployment of small programs
immediate --- master and workers being only distinguished by an
environment variable. \functory\ also allows master and workers to be
completely different programs, which is ideal for large scale deployment.
Another distinguishing feature of our library is a
robust fault-tolerance mechanism which relieves
the user of cumbersome implementation details.
Finally, \functory\ also allows to cascade several distributed
computations inside the same program.

@@

\item 
  Another interesting feature could be the ability
  to add or remove machines dynamically. Currently, our library assumes
  that the list of machines to be used is given \emph{a priori}, as
  part of the code. An alternative would be to read machine names from
  a file, watched periodically by the master.
\item
  Our library provides limited support for displaying real-time
  information about computations and communications. Processing and storing
  information about workers and tasks locally in the master is straightforward; 
  monitoring it in real-time could be done using
  \textsf{Ocamlviz}~\cite{ocamlviz}. 
\item 
  One very nice feature of Google's MapReduce is the possibility to
  use redundantly several idle workers on the same tasks
  for speedup when reaching the end of computation.
  Since we already have the fault tolerance implemented, this
  optimization should be straightforward to add to our library.
\end{itemize}
We intend to enrich our library with all above features.

>>>>

In this paper, we presented a distributed programming library for the
functional programming language \Ocaml. The main features are the
genericity of the interface, which makes use of polymorphic
higher-order functions, and the ability to easily switch between
sequential, multi-core, and network implementations. In particular,
\functory\ allows to use the same executable for master and workers,
which makes the deployment of small programs immediate --- master and
workers being only distinguished by an environment
variable. \functory\ also allows master and workers to be completely
different programs, which is ideal for large scale deployment.
Another distinguishing feature of our library is a robust
fault-tolerance mechanism which relieves the user of cumbersome
implementation details.  Yet another interesting feature of the
library is the ability to add workers dynamically. Finally, \functory\
also allows to cascade several distributed computations inside the
same program.  \functory also implements two levels of API with
different granularities which enables the user to write interactive
programs.

@@

% \item 
%   Another interesting feature could be the ability
%   to add or remove machines dynamically. Currently, our library assumes
%   that the list of machines to be used is given \emph{a priori}, as
%   part of the code. An alternative would be to read machine names from
%   a file, watched periodically by the master.
\item
  Our library provides limited support for displaying real-time
  information about computations and communications. Processing and storing
  information about workers and tasks locally in the master is straightforward; 
  monitoring it in real-time could be done using
  \textsf{Ocamlviz}~\cite{ocamlviz}. 
\item 
  One very nice feature of Google's MapReduce is the possibility to
  use redundantly several idle workers on the same tasks
  for speedup when reaching the end of computation.
  Since we already have the fault tolerance implemented, this
  optimization should be straightforward to add to our library.
\end{itemize}
We intend to enrich our library with all above features.
